### 2022-11-10 briefcommunicaton/briefcommunication.tex
#37: Renamed folder and main file
#37: wordcount with remaining word counter

%% Additional
\usepackage{caption}
%\usepackage{hyperref}

@@

\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

@@

\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.2_boxsize2x2_Ns16_Nvpar48-64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

@@

\nocite{*}
\bibliography{aipsamp}% Produces the bibliography via BibTeX.

>>>>

%% Additional
\usepackage{caption}
\usepackage{hyperref}

@@

%\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

@@

%\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.2_boxsize2x2_Ns16_Nvpar48-64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

@@

\nocite{*}
\bibliography{references.bib}% Produces the bibliography via BibTeX.
